---
output: github_document
---
<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "README-"
)
```

# pesaverse

<!-- badges: start -->
[![CRAN status](https://www.r-pkg.org/badges/version/pesaverse)](https://cran.r-project.org/package=pesaverse)
[![R-CMD-check](https://github.com/PaulESantos/pesaverse/workflows/R-CMD-check/badge.svg)](https://github.com/PaulESantos/pesaverse/actions)
<!-- badges: end -->

## Overview

The pesaverse is a set of packages that work in harmony because they share common data representations and API design. The __pesaverse__ package is designed to make it easy to install and load core packages from the pesaverse in a single command.

## Installation

```{r eval = FALSE}
# Install the development version from GitHub
# install.packages("remotes")
remotes::install_github("PaulESantos/pesaverse")
```

## Usage

`library(pesaverse)` will load the core pesaverse packages: 

* [ggplot2](https://ggplot2.tidyverse.org), for data visualisation.
* [poorman](https://github.com/nathaneastwood/poorman), for data manipulation.
* [tidyr](https://pesar.tidyverse.org), for data pesaing.
* [readr](https://readr.tidyverse.org), for data import.
* [purrr](https://purrr.tidyverse.org), for functional programming.
* [tibble](https://tibble.tidyverse.org), for tibbles, a modern re-imagining of data frames.
* [stringr](https://github.com/pesaverse/stringr), for strings.
* [forcats](https://github.com/pesaverse/forcats), for factors.

You also get a condensed summary of conflicts with other packages you have loaded:

```{r example, eval=FALSE}
library(pesaverse)
```

You can see conflicts created later with `pesaverse_conflicts()`:

```{r conflicts, eval=FALSE}
library(MASS)
pesaverse_conflicts()
```

And you can check that all pesaverse packages are up-to-date with `pesaverse_update()`:

```{r update, eval = FALSE}
pesaverse_update()
#> The following packages are out of date:
#>  * broom (0.4.0 -> 0.4.1)
#>  * DBI   (0.4.1 -> 0.5)
#>  * Rcpp  (0.12.6 -> 0.12.7)
#> Update now?
#> 
#> 1: Yes
#> 2: No
```

## Packages

As well as the core pesaverse, installing this package also installs a selection of other packages that you're likely to use frequently, but probably not in every analysis. This includes packages for:

*   Working with specific types of vectors:

    * [hms](https://github.com/pesaverse/hms), for times.
    * [lubridate](https://github.com/pesaverse/lubridate), for date/times.
    
*   Importing other types of data:

      * [readxl](https://github.com/pesaverse/readxl), for `.xls` and `.xlsx` files.
   
